---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# oisst

<!-- badges: start -->
<!-- badges: end -->

The goal of `oisst` is to easily download [Optimum Interpolation Sea Surface Temperature (OISST)](https://www.ncdc.noaa.gov/oisst) data hosted by National Oceanic and Atmospheric Administration (NOAA). 

## Installation

``` r
remotes::install_github("andybeet/oisst")
```

## Usage

To determine which years have data:

``` {r, eval = T}
oisst::find_years()
```


To download a single years data (year 2001 in example) into a folder called "output" within your current directory

``` 
oisst::get_oisst_data(years=2001,outputStructure=NULL,outputDir=here::here("output"))

```

To download years 2000, ..., 2010 into yearly folders within the "output" folder in current working directory:

```
oisst::get_oisst_data(years=2000:2010,outputStructure="year",outputDir=here::here("output"))
```

To download years 2000, ..., 2005 into a single folder within the "output" folder in current working directory:

```
oisst::get_oisst_data(years=2000:2005,outputStructure=NULL,outputDir=here::here("output"))
```

To download all data into monthly folders within the "output" folder in current working directory:

```
ooist::get_oisst_data(years=NULL,outputStructure="month",outputDir=here::here("output"))
```